{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-07 Notebook LaTEX/Proposal/main.tex
>w<, changes

\section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
    The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
    The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
    \todoinline{\noindent
        Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case.

>>>>

\section{Nestrov's acceleration in the nonconvex case}\label{sec:nes-acc-ncnvx}
    % The behavior of Nesterov's acceleration for function that are nonconvex are the holy grail and the absolute frontier. 
    % The approaches are incredibly diverse and therefore, this section will only list relevant references and briefly mention the ideas involved in those literatures. 
    % \todoinline{\noindent
    %     Here, is a list of early attempted research of Nesterov's acceleration method in the nonconvex case. 
    % }
